MRP Case Study

### 2020-01-31 Code/mrp/Case Study .Rmd
Adding hierarchal stan model and mark down file

  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$cat_pref[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }

  #male or not, eth, age, income level, state, city
  y <- rbinom(n, 1, true_popn$cat_pref[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  income <- poststrat[people, 4]
  state <- poststrat[people, 5]

@@

### Begine Bayseian Work Flow (Modeling) 
We are woking towards building a model that can predict the severity of a service failure baised on consumer feedback. The case study will work to build a simple model and impliment postratification to generalize findings in a sample to a larger population. The model we will focus on here will start as a simple binomial model but we will hopefully build it up. We will be using code taken from Lauren Kenndey and Jonah Gabry's vignette on postratification see: http://mc-stan.org/rstanarm/articles/mrp.html

We will be lookig at the following pices of data about each "customer"

* gender
* age (group)
* income (group)
* state

All of the variables are categorical variables.

WE NEED A MODEL

I HATE RSTANARM -- JUST SAYING

@@

```{r eval = FALSE2}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

@@

```{r eval = FALSE}
sample_popn_pref <- mean(sample$cat_pref)
round(sample_popn_pref, 3)

>>>>

  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_income <- c(0,-0.2, 0.6)
  coef_state <- c(0, round(rnorm(49, 0, 1), 1))
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:5], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$satisfaction[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_income[poststrat[j, 4]] + coef_state[poststrat[j, 5]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
      )
  }

  #male or not, eth, age, income level, state, city
  y <- rbinom(n, 1, true_popn$satisfaction[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  income <- poststrat[people, 4]
  state <- poststrat[people, 5]

@@

```{r echo=FALSE}

J <- c(2, 3, 7, 3, 50) # male or not, eth, age, income level, state
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age","income", "state",'N')
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
        for (i4 in 1:J[4]){
          for (i5 in 1:J[5]){
              count <- count + 1
              # Fill them in so we know what category we are referring to
              poststrat[count, 1:5] <- c(i1-1, i2, i3, i4, i5)
          }
        }
      }
    }
  }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.5, 0.2, 0.3)
  p_age <- c(0.2,.1,0.2,0.2, 0.10, 0.1, 0.1)
  p_income<-c(.50,.35,.15)
  p_state_tmp<-runif(50,10,20)
  p_state<-p_state_tmp/sum(p_state_tmp)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
      p_age[poststrat[j,3]]*p_income[poststrat[j,4]]*p_state[poststrat[j,5]]) #Adjust the N to be the number observed in each category in each group
  }

  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response_inc <- c(1, 0.9, 0.8) / 2.7
  p_response_state <- rbeta(50, 1, 1)
  p_response_state <- p_response_state / sum(p_response_state)
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]] *
      p_response_inc[poststrat[j, 4]] * p_response_state[poststrat[j, 5]]
  }

```

Now that we have our simulated data, we now need our hierarchal stan model.

```{}

// Index values, observations, and covariates.
data {
  int<lower = 1> N;                      // Number of observations.
  int<lower = 1> K;                      // Number of groups.
  int<lower = 1> I;                      // Number of observation-level covariates.

  real satisfaction[N];                        // Vector of observations.
  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
  int eth[N];                               // Vector of ethnicity covariates.
  int age[N];                               // Vector of age covariates.
  int income[N];                          // Vector of income covariates.
  int state[N];                          // Vector of state covariates.

  real gamma_mean;                       // Mean for the hyperprior on gamma.
  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
}

// Parameters and hyperparameters.
parameters {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
  vector[K] beta;                        // Vector of observation-level price coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.
}

// Hierarchical regression.
model {
  // Declare mu for use in the linear model.
  vector[N] mu;

  // Hyperpriors and prior.
  gamma ~ normal(gamma_mean, gamma_var);
  tau ~ uniform(tau_min, tau_max);
  sigma ~ uniform(sigma_min, sigma_max);

  // Population model and likelihood.
  for (k in 1:K) {
    alpha[k,] ~ normal(gamma, tau);
    beta[k] ~ normal(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
  }
  cat_pref ~ normal(mu, sigma);
}

// Generate predictions using the posterior.
generated quantities {
  vector[N] mu_pc;                       // Declare mu for predicted linear model.
  real cat_pref_pc[N];                     // Vector of predicted observations.

  // Generate posterior prediction distribution.
  for (n in 1:N) {
    mu_pc[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    cat_pref_pc[n] = normal_rng(mu_pc[n], sigma);
  }
}

```

As we will also need to do some prior and posterior checks, and for that we will need the generative model.

```{}

// Index values, observations, covariates, and hyperior values.
data {
  int<lower = 1> N;                      // Number of observations.
  int<lower = 1> K;                      // Number of groups.
  int<lower = 1> I;                      // Number of observation-level covariates.

  int<lower = 1, upper = K> male[N];        // Vector of group assignments.
  int eth[N];                               // Vector of ethnicity covariates.
  int age[N];                               // Vector of age covariates.
  int income[N];                          // Vector of income covariates.
  int state[N];                          // Vector of state covariates.

  real gamma_mean;                       // Mean for the hyperprior on gamma.
  real<lower = 0> gamma_var;             // Variance for the hyperprior on gamma.
  real<lower = 0> tau_min;               // Minimum for the hyperprior on tau.
  real<lower = 0> tau_max;               // Maximum for the hyperprior on tau.
  real<lower = 0> sigma_min;             // Minimum for the hyperprior on tau.
  real<lower = 0> sigma_max;             // Maximum for the hyperprior on tau.
}

// Generate data according to the hierarchical regression.
generated quantities {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
  vector[K] beta;                        // Vector of observation-level price coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.

  vector[N] mu;                          // Declare mu for linear model.
  real cat_pref[N];                        // Vector of observations.

  gamma = normal_rng(gamma_mean, gamma_var);
  tau = uniform_rng(tau_min, tau_max);
  sigma = uniform_rng(sigma_min, sigma_max);

  // Draw parameter values and generate data.
  for (k in 1:K) {
    for (i in 1:(I - 1)) {
      alpha[k, i] = normal_rng(gamma, tau);
    }
    beta[k] = normal_rng(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    cat_pref[n] = normal_rng(mu[n], sigma);
  }
}

```

@@

```{r eval = FALSE}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

@@

```{r eval = FALSE}
sample_popn_pref <- mean(sample$satisfaction)
round(sample_popn_pref, 3)
